\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}

\title{AgentStress: A Systematic Taxonomy of Agentic AI Pipeline Failures Under Ambiguous Instructions}
\author{Yash Gupta \\ mryashdev.in \\ research.yashgupta@gmail.com}
\date{May 2026}

\begin{document}

\maketitle

\begin{abstract}
Agentic AI pipelines fail silently and systematically in production, yet no standardized framework exists to detect or classify these failures. This paper introduces AgentStress, an industrial-grade reliability testing framework. We conduct controlled experiments across three instruction clarity levels. Our results identify 7 distinct failure modes and demonstrate how multi-agent networks propagate hallucinations.
\end{abstract}

\section{Introduction}
As AI agents move into production, the risk of unobservable failures increases. Current benchmarks like MMLU focus on model capabilities rather than pipeline reliability. AgentStress addresses this gap...

\section{Related Work}
AgentStress builds upon recent advances in agent evaluation. While \textbf{AgentEval} and \textbf{EvoEval} provide robust frameworks for measuring task completion, they do not systematically classify the \textit{mode} of failure. Our work also complements the multi-agent debate methodology introduced by \textbf{Du et al. (2023)}, but shifts the focus from reasoning improvement to measuring negative externalities like hallucination propagation and overconfidence collapse.

\section{Methodology}
We utilize a 4-round multi-agent debate protocol...
\subsection{Failure Taxonomy}
The framework identifies: Instruction Drift, Premature Termination, Tool Hallucination, Overconfidence Collapse, Stubborn Failure, and Contamination.

\section{Limitations}
We acknowledge that the use of LLMs to judge other agents introduces potential circularity. We mitigate this through objective, checklist-based rubrics. Furthermore, while our 30-task benchmark provides an initial profile, larger-scale datasets are required for definitive statistical power in production settings.

\section{Results}
[Experimental Results Pending Full Execution]

\section{Conclusion}
AgentStress provides a necessary benchmark for agentic reliability and a path toward cryptographically verifiable AI certifications.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
